\mytitle

### 2023-05-11 chapters/jitsynth/overview.tex
Section names
Fix code size for jitsynth

\section{Overview}
\label{s:overview}

@@

\begin{figure}[h]
\centering
\resizebox{\linewidth}{!}{%
\begin{minipage}{1.03\linewidth}
\lstinputlisting[language=rosette,xleftmargin=-.5em,firstline=1,basicstyle=\scriptsize\ttfamily]{code/toy-inputs.rkt}%multicols=2,numbers=left,numbersep=.75em,
\end{minipage}}
\vspace{-.5em}
  \caption{Snippets of inputs to \jitsynth: the interpreters for the source (eBPF) and and target (RISC-V) languages and state-mapping functions.}
  \label{fig:toy-inputs}
  \end{figure}

@@

\begin{lstlisting}[language=rosette,xleftmargin=0em,mathescape=true,basicstyle=\scriptsize\ttfamily]
(define (compile-addi32 s)       ; Returns a list of k instruction holes, to be 
  (define dst (ebpf-insn-dst s)) ; filled with toy RISC-V instructions. Each    
  (define imm (ebpf-insn-imm s)) ; hole represents a set of choices, defined 
  (list (??insn dst imm) ...))   ; by the ??insn procedure.

@@

Given this sketch, and our correctness specification for $C_\cc{addi32}$, the
synthesizer will search the space defined by the sketch for a program that
satisfies the specification.
%
Below is an example of the resulting toy compiler from eBPF to
RISC-V, synthesized and translated to C by \jitsynth (without the
outer loop):\tighten
\lstinputlisting[language=C,xleftmargin=2em,firstline=1,basicstyle=\scriptsize\ttfamily]{code/toy-compiler.c}%multicols=2,numbers=left,numbersep=.75em,

>>>>

\section{\jitsynth in a nutshell}% TODO bad name
\label{s:overview}

@@

\begin{figure}[h]
\centering
\resizebox{\linewidth}{!}{%
\begin{minipage}{1.03\linewidth}
\lstinputlisting[language=rosette,xleftmargin=-.5em,firstline=1]{code/toy-inputs.rkt}%multicols=2,numbers=left,numbersep=.75em,
\end{minipage}}
\vspace{-.5em}
  \caption{Snippets of inputs to \jitsynth: the interpreters for the source (eBPF) and and target (RISC-V) languages and state-mapping functions.}
  \label{fig:toy-inputs}
  \end{figure}

@@

\begin{lstlisting}[language=rosette,xleftmargin=0em,mathescape=true]
(define (compile-addi32 s)       ; Returns a list of k instruction holes, to be 
  (define dst (ebpf-insn-dst s)) ; filled with toy RISC-V instructions. Each    
  (define imm (ebpf-insn-imm s)) ; hole represents a set of choices, defined 
  (list (??insn dst imm) ...))   ; by the ??insn procedure.

@@

Given this sketch, and our correctness specification for $C_\cc{addi32}$, the
synthesizer will search the space defined by the sketch for a program that
satisfies the specification.
%
Below is an example of the resulting toy compiler from eBPF to
RISC-V, synthesized and translated to C by \jitsynth (without the
outer loop):\tighten
\lstinputlisting[language=C,xleftmargin=2em,firstline=1]{code/toy-compiler.c}%multicols=2,numbers=left,numbersep=.75em,
